Assignment 1: Data and Descriptive

### 2023-10-12 MSB104_assignment1.qmd
Second draft of final draft 12.10.23

---
title: "Assignment 1: Data and Descriptive"
author: "Asbjørn Gaard & René Rødde Bracci"
format: html
editor: visual
bibliography: [MSB104_Assignment1.bib]
---

@@

@@

>>>>

---
title: "Assignment 1: Data and Descriptive"
author: "Asbjørn Gaard & René Rødde Bracci"
format: pdf
editor: visual
bibliography: [MSB104_Assignment1.bib]
---

@@

```{r}
#| echo: false
# To ensure the table do not contain previous grouping, we use the ungroup function. Moreover, we select desirable variable. Additional, the st fuction is utilised to compute summary statistics for the selected columns. Lastly, the summ-fuction specifies the summary statistics to calculate
GDP_DE_nuts2 |> 
  ungroup() |> 
  select(Year, GDP_pc = GDP_per_capita_nuts2_DE) |> 
  st(group = "Year", group.long = TRUE, 
     summ = c('notNA(x)','mean(x)', 'median(x)', 
              'sd(x)','min(x)','max(x)'),
     )

```

@@

# Appendix
